---
title: "P8105_hm1_kh3074"
output: github_document
---
```{r}
#import all the packages needed
library(tidyverse)
library(palmerpenguins)
```

---

# Problem 1 

## Create dataframe
```{r}
p1_var1 = rnorm(10,mean = 0,sd = 1)
#create a random sample of size 10 from a standard Normal distribution
p1_var2 = p1_var1 > 0 
#create a logical vector indicating whether elements of the sample are greater than 0
p1_var3 = c('I','love','pancake','and','I','don\'t','know','what','I\'m','saying')
#create a character vector of length 10
p1_var4 = factor(c('old','young','baby','old','young','baby','old','young','baby','young'))
#a factor vector of length 10, with 3 different factor “levels”
p1_df = tibble(
  p1_var1,
  p1_var2,
  p1_var3,
  p1_var4
)
#put all the four variables in to a dataframe
p1_df
```
## caculate mean
```{r}
for (i in 1:length(p1_df)){
  tryCatch({cat('mean of',colnames(p1_df)[i],'is',mean(pull(p1_df,i)),'\n')}, 
           #try calculate mean for ith variable in p1_df
           warning = function(w){
           cat(colnames(p1_df)[i],'variable in the dataframe doesn\'t work for mean','\n')
           #show the variable name if it doesn't work for mean
           }
  )
}
```

## try convert variables to numeric
```{r, results='hide'}
as.numeric(0.3)
as.numeric(TRUE)
as.numeric('pancake')
as.numeric(factor('old','young'))
```


Float variable and logistic variable can successfully convert to numeric variables  
Factor variable and character variable get NA  
Conclusion: character and factor can't convert to numeric variables so they don't work for mean  


---
# Problem 2

## load penguins dataset
```{r}
df = data(penguins,package = 'palmerpenguins')
penguins
summary(penguins)
```
## describe the dataset
```{r}
colnames(penguins)
```
here are total 344 penguins in the data set and each of them have 8 features
```{r}
table(penguins[1])
```
species is a **factor** variables which contain 3 "levels",there are 152 Adelies,68 Chinstraps and 124 Gentoos 
```{r}
table(penguins[2])
```
island  is a **factor** variables which contain 3 "levels",there are 168 Biscoe,124 Dream and 52 Torgersen 

```{r}
sum(is.na(pull(penguins,3)))
#find the missing value
```

"bill_length_mm"and "bill_depth_mm"are **float** variables  
"flipper_length_mm"and "body_mass_g" are **int** variables  
**There are two penguins lost these four values**
```{r}
sum(is.na(pull(penguins,7)))
```

sex is a **factor** variable which contain 2 "levels",there are 165 femals,and 168 males **(11 NAs)**
```{r}
table(penguins[8])
```
All the penguins are observed during 2007,2008,2009

## The size of the dataset
```{r}
ncol(penguins)
nrow(penguins)
```
There are **344** penguins recorded and each of them have **8** features 

## The mean of flipper length

**there are 2 missing values in the vector "flipper_length_mm"**
We should ignore the two missing values when we calculate the mean.
```{r}
mean(pull(penguins,5),na.rm = TRUE)
```
The mean flipper length is 200.9152

## Draw the scatterplot
```{r}
ggplot(penguins,aes(x = bill_length_mm,y = flipper_length_mm, colour = species)) + geom_point()
ggsave('penguin plot.png')
```






